Congress text mining

### 2022-11-29 slides/slides.qmd
push slides2

---
title: "Congress text mining"
title-slide-attributes:
    data-background-image: /layout/background.jpg
    title-slide-style: 
subtitle: "Text as Data Assignment 3"
date: 01.12.2022
format:
    revealjs:
        code-fold: true
        code-tools: true
        theme: sky
        slide-number: true
        preview-links: auto
        footer: "[github.com/juka19/tad_assignment3](https://github.com/juka19/tad_assignment3)"
        transition: slide
        transition-speed: fast
        background-transition: fade
filters:
    - reveal-auto-agenda
    - designmode
auto-agenda:
    bullets: numbered
    heading: Agenda
auto-play-media: true
---

@@

```{.python}
import plotly.express as px
import pandas as pd

df = pd.read_csv("data\\data_28_11_sponsors.csv")

```

>>>>

---
title: "Congress text mining"
title-slide-attributes:
    data-background-image: /layout/background.jpg
    title-slide-style: 
subtitle: "Text as Data Assignment 3"
date: 01.12.2022
format:
    revealjs:
        code-fold: true
        code-tools: true
        theme: sky
        slide-number: true
        preview-links: auto
        footer: "[github.com/juka19/tad_assignment3](https://github.com/juka19/tad_assignment3)"
        transition: slide
        transition-speed: fast
        background-transition: fade
filters:
    - reveal-auto-agenda
    - designmode
auto-agenda:
    bullets: numbered
    heading: Agenda
auto-play-media: true
jupyter: python3
---

@@

## Share of Cosponsors across Policy fields

```{python, fullscreen=true}
import plotly.io as pio
fig = pio.read_json('plots\\polar_line_plot')
fig.show()
```
